### 2022-01-21 appendix4/appendix.tex
.

%!TEX root = ../thesis.tex
\chapter{Kronecker properties}\label{appendix: kronecker}
Here we detail some properties of Kronecker sum, products, and exponentials (see \citep{MEinAP}, Appendix A.4).

Let 
\[\bs A = \left[\begin{array}{ccc}a_{11} & \dots & a_{1m}\\\hdots & & \hdots \\ a_{n1}&\dots & a_{nm}\end{array}\right]
\qquad
\bs{B} = \left[\begin{array}{ccc}b_{11} & \dots & b_{1m'}\\\hdots & & \hdots \\ b_{n'1}&\dots & b_{n'm'}\end{array}\right]\]
be matrices. The operator \(\otimes\) is the Kronecker product of two matrices; 
\[\bs A\otimes \bs{B} = \left[\begin{array}{ccc}a_{11}\bs{B} & \dots & a_{1m}\bs{B}\\\hdots & & \hdots \\ a_{n1}\bs{B}&\dots & a_{nm}\bs{B}\end{array}\right],\]
which is an \(nn'\times mm'\) matrix.

@@

@@

\begin{lem}\label{lem: lst mpr}
	Let \(\bs{T}\) and \(\bs{C}\) be \(n\times n\), square matrices with \(\bs{C}\) diagonal and invertible; let \(\bs{S}\) be a \(p\times p\) matrix. Further, suppose \(\left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]\) is invertible for \(\lambda>0\). Then
\begin{align}
	&\int_{t=0}^\infty e^{-\lambda t}  e^{{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t}} \wrt t 
	%
	=   \int_{x=0}^\infty e^{{\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)x}}\otimes e^{\bs{S}x} \wrt x \left(\bs{C}\otimes \bs{I}\right)^{-1}  \label{eqn:lstsimplify}\end{align}
\end{lem}
\begin{proof}
	Computing the integral on the left-hand side and then factorising the result and using the \ref{eqn:mpr} multiple times gives
	\begin{align}
            	\int_{t=0}^\infty e^{-\lambda t} e^{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t} \wrt t\nonumber 
            	%
            	&= - \left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]^{-1}
		%
		\\&= -  \left[\bs{T}\otimes \bs{I} + \left(\bs{C}\otimes \bs{I}\right)\left(\bs{I}\otimes \bs{S}\right) - \lambda \bs{I}\right]^{-1}\nonumber
		%
		\\&= -  \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}\otimes \bs{I}\right)^{-1}\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}\otimes \bs{I}\right)^{-1}\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 12}
		%
	\end{align}
	By Equation~(\ref{eqn:kron inverse}) and since \(\bs{C}\) is invertible, (\ref{eqn: ref this one 12}) is equal to
	\begin{align}
		& - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\otimes \bs{I}\right)\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\otimes \bs{I}\right)\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 13}
		%
	\end{align}
	{Using the \ref{eqn:mpr} and algebraic manipulation, (\ref{eqn: ref this one 13}) is equal to }
	\begin{align}
		&- \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\bs{T}\right)\otimes \bs{I} + \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\lambda \bs{I}\right)\otimes \bs{I}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1} \nonumber
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\oplus \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1},\label{eqn: is an integral}
	\end{align}
	by definition of the Kronecker sum.

@@

The exponential of a matrix \(\bs B\) is \[e^{\bs B} := \sum_{n=0}^\infty \cfrac{1}{n!}B^n.\]

\cite{ln2015} show the following.
\begin{lem}\label{lem: sfkjgn}
	Let \(\bs B\) be the block-partitioned matrix
	\[\bs B = \left[\begin{array}{cc} \bs B_{11} & \bs B_{12} \\ \bs B_{21} & \bs B_{22} \end{array}\right]\]
	where \(\bs B_{11}\) and \(\bs B_{22}\) are matrices of order \(m_1\) and \(m_2\), respectively. Denote by \(\bs H_{11}(t)\) the top-left quadrant of order \(m_1\) of \(e^{\bs Bt}\):
	\[\bs H_{11}(t) = \vligne{\bs I_{m_1\times m_1} & \bs 0} e^{\bs Bt}\left[\begin{array}{c}\bs I_{m_1\times m_1} \\ \bs 0\end{array}\right].\]

	The matrix \(\bs H_{11}(t)\) is the solution of 
	\begin{align}\label{eqn: akg987LKJ}
		\bs H_{11}(t) = e^{\bs B_{11}t} + \int_{v=0}^t\int_{u=v}^t e^{\bs B_{11}(t-u)}\bs B_{12}e^{\bs B_{22}(u-v)}\bs B_{21}\bs H_{11}(v)\wrt u\wrt v.
	\end{align}
\end{lem}

@@

\begin{cor}\label{cor: mpr B}
	For \(m\in\{+,-\}\) the top-left quadrant of size \(m_1\times m_1=|\calS_m|\cdot p \times |\calS_m|\cdot p\) of \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I & \bs 0}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t\left[\begin{array}{c} \bs I \\ \bs 0 \end{array}\right], \nonumber
	\end{align}
	is given by 
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm} (\lambda)x}\otimes  e^{\bs S x}\wrt x(\bs C_m^{-1}\otimes \bs I).\label{eqn: skagh87} 
	\end{align}
	For \(m\in\{+,-\}\) the top-right quadrant of size \(m_1\times m_2=|\calS_m|\cdot p\times |\calS_0|\cdot p\) of  \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I & \bs 0}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t \left[\begin{array}{c}\bs 0 \\ \bs I\end{array}\right] ,\nonumber
	\end{align}
	is given by
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x((\bs C_m^{-1}\bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1})\otimes \bs I).\label{eqn: skagh873} 
	\end{align}
	Also, 
	\begin{align}
		&\vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t \bs{B}_{m{n}} %= \vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t  \left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
	= \int_{x=0}^\infty \bs H^{mn}(\lambda,x)  \otimes  e^{\bs S x}\bs D\wrt x\left(\vligne{\bs I_{pn} & \bs 0_{pn\times p|\calS_0|}}\right), \label{eqn: akgj987adKLDJ}
\end{align}
for \(m,n\in\{+,-\}\), \(m\neq n\).
\end{cor}
\begin{proof}
	From Lemma~\ref{lem: sfkjgn} the top-left quadrant of size \(m_1\times m_1=|\calS_m|\cdot p \times |\calS_m|\cdot p\) of the integral with respect to \(t\) on the left-hand side of (\ref{eqn: skagh87}) is 
	\begin{align}
		\int_{t=0}^\infty e^{\left(\bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S - \lambda \bs I+ (\bs T_{m0}\otimes \bs I)(\lambda \bs I-\bs T_{00}\otimes \bs I)^{-1}(\bs T_{0m}\otimes \bs I)\right)t}\wrt t. \label{eqn: akjf768}
	\end{align}
	By Lemma~\ref{lem: lst mpr}, (\ref{eqn: akjf768}) is equal to 
	\begin{align}
		&\int_{x=0}^\infty e^{\bs C_m^{-1}\left(\bs T_{mm} - \lambda \bs I+ \bs T_{m0} (\lambda \bs I-\bs T_{00})^{-1}\bs T_{0m} \right)x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1}\nonumber
		%
		\\&=\int_{x=0}^\infty e^{\bs Q_{mm} ( \lambda )x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1} , \label{eqn: akjf7623988}
	\end{align}
	from the definition of \(\bs Q_{mm}(\lambda)\). This proves (\ref{eqn: skagh87}).

@@

Now, using (\ref{eqn: skagh87}) and (\ref{eqn: skagh873}) we can write 
\begin{align}
	\nonumber&\vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t \bs{B}_{m{n}} = \vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t  \left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
	%
%	\\\nonumber& =\left[ \begin{array}{cc} \displaystyle \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x(\bs C_m^{-1} \otimes \bs I) & \displaystyle \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x((\bs C_m^{-1}\bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1})\otimes \bs I)  \end{array}\right]
%	\\\nonumber&\quad\times\left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
	%
	\\&= \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x (\bs C_m^{-1}(\bs{T}_{mn} + \bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1}\bs T_{0n}) \vligne{\bs I_n & \bs 0_{n\times |\calS_0|}} \otimes \bs D) \nonumber
	%
	\\&= \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x \left( \left( \bs{Q}_{mn} (\lambda) \vligne{\bs I_n & \bs 0_{n\times |\calS_0|}} \right) \otimes \bs D\right)  \nonumber
	%
	\\&= \int_{x=0}^\infty \left(\bs H^{mn}(\lambda,x) \vligne{\bs I_n & \bs 0_{n\times |\calS_0|}}\right) \otimes  e^{\bs S x}\bs D\wrt x,\nonumber
	%
	\\&= \int_{x=0}^\infty \bs H^{mn}(\lambda,x)  \otimes  e^{\bs S x}\bs D\wrt x,\vligne{\bs I_{pn} & \bs 0_{pn\times p|\calS_0|}} \label{eqn: akgj987ad}
\end{align}
for \(m,n\in\{+,-\}\), \(m\neq n\) which is (\ref{eqn: akgj987adKLDJ}), where the last line holds from the \ref{eqn:mpr}. 
\end{proof}

>>>>

%!TEX root = ../thesis.tex
\chapter{Kronecker properties}\label{appendix: kronecker}
Here we detail some properties of Kronecker sums, products, and exponential (see \citep{MEinAP}, Appendix A.4).

Let 
\[\bs A = \left[\begin{array}{ccc}a_{11} & \dots & a_{1m}\\\hdots & & \hdots \\ a_{n1}&\dots & a_{nm}\end{array}\right]
\qquad
\bs{B} = \left[\begin{array}{ccc}b_{11} & \dots & b_{1m'}\\\hdots & & \hdots \\ b_{n'1}&\dots & b_{n'm'}\end{array}\right]\]
be matrices with dimensions \(n\times m\) and \(n'\times m'\), respectively. The operator \(\otimes\) is the Kronecker product of two matrices; 
\[\bs A\otimes \bs{B} = \left[\begin{array}{ccc}a_{11}\bs{B} & \dots & a_{1m}\bs{B}\\\hdots & & \hdots \\ a_{n1}\bs{B}&\dots & a_{nm}\bs{B}\end{array}\right],\]
which is an \(nn'\times mm'\) matrix.

@@

The exponential of a square matrix \(\bs B\) is \[e^{\bs B} := \sum_{n=0}^\infty \cfrac{1}{n!}\bs B^n.\]

@@

\begin{lem}\label{lem: lst mpr}
	Let \(\bs{T}\) and \(\bs{C}\) be \(n\times n\), square matrices with \(\bs{C}\) diagonal and invertible; let \(\bs{S}\) be a \(p\times p\) matrix. Further, suppose \(\left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]\) is invertible for \(\lambda>0\). Then
\begin{align}
	&\int_{t=0}^\infty e^{-\lambda t}  e^{{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t}} \wrt t 
	%
	=   \int_{x=0}^\infty e^{{\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)x}}\otimes e^{\bs{S}x} \wrt x \left(\bs{C}\otimes \bs{I}\right)^{-1}.  \label{eqn:lstsimplify}\end{align}
\end{lem}
\begin{proof}
	Computing the integral on the left-hand side and then factorising the result and using the \ref{eqn:mpr} multiple times gives
	\begin{align}
            	\int_{t=0}^\infty e^{-\lambda t} e^{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t} \wrt t\nonumber 
            	%
            	&= - \left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]^{-1}
		%
		\\&= -  \left[\bs{T}\otimes \bs{I} + \left(\bs{C}\otimes \bs{I}\right)\left(\bs{I}\otimes \bs{S}\right) - \lambda \bs{I}\right]^{-1}\nonumber
		%
		\\&= -  \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}\otimes \bs{I}\right)^{-1}\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}\otimes \bs{I}\right)^{-1}\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 12}
		%
	\end{align}
	By Equation~(\ref{eqn:kron inverse}) and since \(\bs{C}\) is invertible, (\ref{eqn: ref this one 12}) is equal to
	\begin{align}
		& - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\otimes \bs{I}\right)\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\otimes \bs{I}\right)\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 13}
		%
	\end{align}
	{Using the \ref{eqn:mpr} and algebraic manipulation, (\ref{eqn: ref this one 13}) is equal to }
	\begin{align}
		&- \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\bs{T}\right)\otimes \bs{I} + \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\lambda \bs{I}\right)\otimes \bs{I}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1} \nonumber
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\oplus \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1},\label{eqn: is an integral}
	\end{align}
	by definition of the Kronecker sum.

@@

\begin{lem}[\cite{ln2015}]\label{lem: sfkjgn}
	Let \(\bs B\) be the block-partitioned matrix
	\[\bs B = \left[\begin{array}{cc} \bs B_{11} & \bs B_{12} \\ \bs B_{21} & \bs B_{22} \end{array}\right]\]
	where \(\bs B_{11}\) and \(\bs B_{22}\) are matrices of order \(m_1\) and \(m_2\), respectively. Denote by \(\bs H_{11}(t)\) the top-left quadrant of order \(m_1\) of \(e^{\bs Bt}\):
	\[\bs H_{11}(t) = \vligne{\bs I_{m_1\times m_1} & \bs 0} e^{\bs Bt}\left[\begin{array}{c}\bs I_{m_1\times m_1} \\ \bs 0\end{array}\right].\]

	The matrix \(\bs H_{11}(t)\) is the solution of 
	\begin{align}\label{eqn: akg987LKJ}
		\bs H_{11}(t) = e^{\bs B_{11}t} + \int_{v=0}^t\int_{u=v}^t e^{\bs B_{11}(t-u)}\bs B_{12}e^{\bs B_{22}(u-v)}\bs B_{21}\bs H_{11}(v)\wrt u\wrt v.
	\end{align}
\end{lem}
\begin{proof}
	See \cite{ln2015}.
\end{proof}

@@

Now, recall the matrix-functions
\begin{align*}
	% \bs Q_{+0}(\lambda) &= \bs C_+^{-1}\bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1},
	% %
	% \\\bs Q_{-0}(\lambda) &= \bs C_-^{-1}\bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1},
	%
	\bs Q_{++}(\lambda) &= \bs C_+^{-1} \left(\bs T_{++} - \lambda \bs I + \bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0+}\right),
	%
	\\\bs Q_{+-}(\lambda) &= \bs C_+^{-1} \left(\bs T_{+-} + \bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0-} \right) ,
	%
	\\\bs Q_{--}(\lambda) &= \bs C_-^{-1} \left(\bs T_{--}  - \lambda \bs I + \bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0-}\right),
	%
	\\\bs Q_{-+}(\lambda) &=\bs C_-^{-1} \left(\bs T_{-+}+ \bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0+}\right) ,
\end{align*}
from Chapter~\ref{sec: conv}.
\begin{cor}\label{cor: mpr B}
	For \(m\in\{+,-\}\) the top-left quadrant of size \(m_1\times m_1=|\calS_m|\cdot p \times |\calS_m|\cdot p\) of \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I & \bs 0}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t\left[\begin{array}{c} \bs I \\ \bs 0 \end{array}\right], \nonumber
	\end{align}
	is given by 
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm} (\lambda)x}\otimes  e^{\bs S x}\wrt x(\bs C_m^{-1}\otimes \bs I).\label{eqn: skagh87} 
	\end{align}
	For \(m\in\{+,-\}\) the top-right quadrant of size \(m_1\times m_2=|\calS_m|\cdot p\times |\calS_0|\cdot p\) of  \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I & \bs 0}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t \left[\begin{array}{c}\bs 0 \\ \bs I\end{array}\right] ,\nonumber
	\end{align}
	is given by
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x((\bs C_m^{-1}\bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1})\otimes \bs I).\label{eqn: skagh873} 
	\end{align}
	Also, 
	\begin{align}
		&\vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t \bs{B}_{m{n}} %= \vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t  \left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
	= \int_{x=0}^\infty \bs H^{mn}(\lambda,x)  \otimes  e^{\bs S x}\bs D\wrt x\left(\vligne{\bs I_{pn} & \bs 0_{pn\times p|\calS_0|}}\right), \label{eqn: akgj987adKLDJ}
\end{align}
for \(m,n\in\{+,-\}\), \(m\neq n\).
\end{cor}
\begin{proof}
	From Lemma~\ref{lem: sfkjgn} the top-left quadrant of size \(m_1\times m_1=|\calS_m|\cdot p \times |\calS_m|\cdot p\) of the integral with respect to \(t\) on the left-hand side of (\ref{eqn: skagh87}) is 
	\begin{align}
		\int_{t=0}^\infty e^{\left(\bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S - \lambda \bs I+ (\bs T_{m0}\otimes \bs I)(\lambda \bs I-\bs T_{00}\otimes \bs I)^{-1}(\bs T_{0m}\otimes \bs I)\right)t}\wrt t. \label{eqn: akjf768}
	\end{align}
	By Lemma~\ref{lem: lst mpr}, (\ref{eqn: akjf768}) is equal to 
	\begin{align}
		&\int_{x=0}^\infty e^{\bs C_m^{-1}\left(\bs T_{mm} - \lambda \bs I+ \bs T_{m0} (\lambda \bs I-\bs T_{00})^{-1}\bs T_{0m} \right)x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1}\nonumber
		%
		\\&=\int_{x=0}^\infty e^{\bs Q_{mm} ( \lambda )x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1} , \label{eqn: akjf7623988}
	\end{align}
	from the definition of \(\bs Q_{mm}(\lambda)\). This proves (\ref{eqn: skagh87}).

@@

Now, using (\ref{eqn: skagh87}) and (\ref{eqn: skagh873}) we can write 
\begin{align}
	\nonumber&\vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t \bs{B}_{m{n}} = \vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t  \left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
	%
%	\\\nonumber& =\left[ \begin{array}{cc} \displaystyle \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x(\bs C_m^{-1} \otimes \bs I) & \displaystyle \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x((\bs C_m^{-1}\bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1})\otimes \bs I)  \end{array}\right]
%	\\\nonumber&\quad\times\left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
	%
	\\&= \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x (\bs C_m^{-1}(\bs{T}_{mn} + \bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1}\bs T_{0n}) \vligne{\bs I_n & \bs 0_{n\times |\calS_0|}} \otimes \bs D) \nonumber
	%
	\\&= \int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x \left( \left( \bs{Q}_{mn} (\lambda) \vligne{\bs I_n & \bs 0_{n\times |\calS_0|}} \right) \otimes \bs D\right)  \nonumber
	%
	\\&= \int_{x=0}^\infty \left(\bs H^{mn}(\lambda,x) \vligne{\bs I_n & \bs 0_{n\times |\calS_0|}}\right) \otimes  e^{\bs S x}\bs D\wrt x,\nonumber
	%
	\\&= \int_{x=0}^\infty \bs H^{mn}(\lambda,x)  \otimes  e^{\bs S x}\bs D\wrt x,\vligne{\bs I_{pn} & \bs 0_{pn\times p|\calS_0|}}, \label{eqn: akgj987ad}
\end{align}
for \(m,n\in\{+,-\}\), \(m\neq n\) which is (\ref{eqn: akgj987adKLDJ}), where the last line holds from the \ref{eqn:mpr}. 
\end{proof}
